Constraint Programming Algorithms used in Gecode

### 2014-05-19 paper.tex
added objective functions

	In the following I will explain the necessary steps to describe and solve a problem with constraint programming: variables, constraints, search trees, constraint propagation and search algorithms. As example of an implementation I will refer to \emph{Gecode} \cite{gecode}.

@@

>>>>

	In the following I will explain the necessary steps to describe and solve a problem with constraint programming: variables, constraints, objective functions, search trees, constraint propagation and search algorithms. As example of an implementation I will refer to \emph{Gecode} \cite{gecode}.

@@

	\subsection{Objective Functions}
	A constraint problem can have, additional to constraints, an objective function. As in optimization only one objective function can be optimized at a time, a problem in constraint programming must have either one or no objective function. To solve problems with an objective function it is necessary to select a search algorithm which is capable of optimization.
